---
Title: Resume Comparison Analysis
Date of analysis: March 30, 2020
Purpose: Comparing reviewer impressions of 3 resumes
Data collected from: Amazon Mechanical Turk
output: word_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(out.height = "\\textheight",  out.width = "\\textwidth")
knitr::opts_chunk$set(echo=FALSE) 
knitr::opts_knit$set(root.dir=dirname(rstudioapi::getSourceEditorContext()$path)) 
```

# Study Design
Title: Resume Comparison Analysis

Date of analysis: March 30, 2020

Purpose: Comparing reviewer impressions of 3 resumes

Data collected from: Amazon Mechanical Turk



```{r Import dataset, include=FALSE, echo=TRUE}
# Import dataset
library(readxl)
library(Hmisc)
library(dplyr)
library(psych)
library(car)
library(emmeans)
library(phia)
library(kableExtra)
library(BayesFactor)
library(knitr)
library(dunn.test)

ResumeDataRaw <- read_excel("Developing+Resume+Pretest+IV_December+7,+2020_16.27.xlsx")
```


# Frequencies
```{r Frequencies, include=FALSE}
# apply(ResumeDataRaw[, 7:70], 2, table)
# hist.data.frame(ResumeDataRaw[,7:70], title = "Histograms of all Numeric Variables")
```


```{r Recoding gender, include=FALSE}
## Recoding gender

dplyr::count(ResumeDataRaw, gender, gender_4_TEXT)
ResumeDataRaw$GenderRecoded <- ResumeDataRaw$gender %>%
  factor(levels=c(1,2,3,4),
         labels=c("Man", "Woman", "Non-Binary", "I use another term / Option no listed"))
dplyr::count(ResumeDataRaw, GenderRecoded, gender, gender_4_TEXT)
```


```{r Recoding race, include=FALSE}
## Recoding race 
ResumeDataRaw %>%
    select(race, race_8_TEXT) %>%
    filter(!is.na(race_8_TEXT))

ResumeDataRaw <- ResumeDataRaw %>%
  mutate(RaceRecoded=case_when(grepl(",", race) ~ "10",
                                 race_8_TEXT == "Caucasian/ European American"  ~ "5",
                                 TRUE ~ race))
ResumeDataRaw$RaceRecoded <- ResumeDataRaw$RaceRecoded %>%
  factor(levels=c(1,2,3,4,5,6,7,8,10),
         labels=c("Black/African American", "Asian/Asian American", "Latino/a/Hispanic/Latin American", "Native American/American Indian/Alaskan Native", "White", "Native Hawaiian/Pacific Islander", "Middle Eastern/Middle Eastern American", "Other", "More than one race"))
dplyr::count(ResumeDataRaw, RaceRecoded, race, race_8_TEXT)
```




```{r Exclusions, include=FALSE}
## Check if all participants consented
plyr::count(ResumeDataRaw$ConsentQ)
ResumeDataClean <- ResumeDataRaw %>% 
  mutate(ConsentRecoded=ConsentQ)
ResumeDataClean$ConsentRecoded <- ResumeDataClean$ConsentRecoded %>% 
  factor(levels=c(1,2),
         labels=c("I consent to participate in this research study", "I do not consent to participate in this research study"))
plyr::count(ResumeDataClean$ConsentRecoded)
## Note: All participants consented to participate in the study

## Check if any participants didn't answer any manipulation questions 
which(colnames(ResumeDataClean)=="attDesResA")
which(colnames(ResumeDataClean)=="livedUS_2")

ResumeDataCleanExclusions <- ResumeDataClean %>%
  filter(rowSums(!is.na(ResumeDataClean[ ,8:68])) > 0)
nrow(ResumeDataCleanExclusions)
## All participants answered at least one question on the survey
```


```{r Preparing dataset for analysis, include=FALSE}
## Creating a condition variable 
ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>%
  mutate(ConditionA=if_else(rowSums(!is.na(ResumeDataCleanExclusions[ ,8:25])) > 0, "ConditionA", "NA"),
         ConditionB=if_else(rowSums(!is.na(ResumeDataCleanExclusions[ ,26:43])) > 0, "ConditionB", "NA"),
         ConditionC=if_else(rowSums(!is.na(ResumeDataCleanExclusions[ ,44:61])) > 0, "ConditionC", "NA"))

ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>% 
  mutate(Condition=case_when(ConditionA == "ConditionA" ~ "ConditionA",
                               ConditionB == "ConditionB" ~ "ConditionB",
                               ConditionC == "ConditionC" ~ "ConditionC"))
plyr::count(ResumeDataCleanExclusions$Condition)

## Combining variables across resumes and reverse coding variables
ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>% 
  mutate(attDesRes=coalesce(attDesResA, attDesResB, attDesResC),
         likelyAmRes=coalesce(likelyAmResA, likelyAmResB, likelyAmResC),
         natEngSkillRes=coalesce(natEngSkillResA, natEngSkillResB, natEngSkillResC),
         famAmCustRes=coalesce(famAmCustResA, famAmCustResB, famAmCustResC),
         amCultKnRes=coalesce(amCultKnResA, amCultKnResB, amCultKnResC),
         forAccRes=coalesce(forAccResA, forAccResB, forAccResC),
         natEngSpRes=coalesce(natEngSpResA, natEngSpResB, natEngSpResC),
         wellEdRes=coalesce(wellEdResA, wellEdResB, wellEdResC),
         compRes=coalesce(compResA, compResB, compResC),
         critThinkRes=coalesce(critThinkResA, critThinkResB, critThinkResC),
         profSkillRes=coalesce(profSkillResA, profSkillResB, profSkillResC),
         highStatRes=coalesce(highStatResA, highStatResB, highStatResC),
         profCarRes=coalesce(profCarResA, profCarResB, profCarResC),
         qualRes=coalesce(qualResA, qualResB, qualResC),
         friendRes=coalesce(friendResA, friendResB, friendResC),
         moralRes=coalesce(moralResA, moralResB, moralResC),
         libRes=coalesce(libResA, libResB, libResC),
         conservRes=coalesce(conservResA, conservResB, conservResC),
         ForAccARecoded=8-forAccResA,
         ForAccBRecoded=8-forAccResB,
         ForAccCRecoded=8-forAccResC,
         LibResARecoded=8-libResA,
         LibResBRecoded=8-libResB,
         LibResCRecoded=8-libResC,
         ForAccRecoded=8-forAccRes,
         LibResRecoded=8-libRes)
```



```{r Calculating reliability and composite variables, include=FALSE}
# Cronbach's Alpha 

## Americanness for each resume
AmericanAlphaResA <- psych::alpha(ResumeDataCleanExclusions[c("likelyAmResA", "natEngSkillResA", "famAmCustResA", "amCultKnResA", "ForAccARecoded", "natEngSpResA")])
AmericanAlphaResA$total

AmericanAlphaResB <- psych::alpha(ResumeDataCleanExclusions[c("likelyAmResB", "natEngSkillResB", "famAmCustResB",
                                                      "amCultKnResB", "ForAccBRecoded", "natEngSpResB")])
AmericanAlphaResB$total

AmericanAlphaResC <- psych::alpha(ResumeDataCleanExclusions[c("likelyAmResC", "natEngSkillResC", "famAmCustResC",
                                                      "amCultKnResC", "ForAccCRecoded", "natEngSpResC")])
AmericanAlphaResC$total


## Status for each resume
StatusAlphaResA <- psych::alpha(ResumeDataCleanExclusions[c("wellEdResA", "compResA", "critThinkResA",
                                                      "profSkillResA", "highStatResA", "profCarResA",
                                                    "qualResA")])
StatusAlphaResA$total

StatusAlphaResB <- psych::alpha(ResumeDataCleanExclusions[c("wellEdResB", "compResB", "critThinkResB",
                                                    "profSkillResB", "highStatResB", "profCarResB",
                                                    "qualResB")])
StatusAlphaResB$total

StatusAlphaResC <- psych::alpha(ResumeDataCleanExclusions[c("wellEdResC", "compResC", "critThinkResC",
                                                    "profSkillResC", "highStatResC", "profCarResC",
                                                    "qualResC")])
StatusAlphaResC$total

# Split-Half Reliability (Using Spearman-Brown prediction formula)

## Warmth for each resume
which(colnames(ResumeDataCleanExclusions)=="friendResA")
which(colnames(ResumeDataCleanExclusions)=="moralResA")
outputWarmthResA <- splitHalf(ResumeDataCleanExclusions[,22:23])
outputWarmthResA$meanr

which(colnames(ResumeDataCleanExclusions)=="friendResB")
which(colnames(ResumeDataCleanExclusions)=="moralResB")
outputWarmthResB <- splitHalf(ResumeDataCleanExclusions[,40:41])
outputWarmthResB$meanr

which(colnames(ResumeDataCleanExclusions)=="friendResC")
which(colnames(ResumeDataCleanExclusions)=="moralResC")
outputWarmthResC <- splitHalf(ResumeDataCleanExclusions[,58:59])
outputWarmthResC$meanr


## Political orientation for each resume
polOrientSidebySideResA <- select(ResumeDataCleanExclusions, LibResARecoded, conservResA)
outputPolOrientResA <- splitHalf(polOrientSidebySideResA)
outputPolOrientResA$meanr

polOrientSidebySideResB <- select(ResumeDataCleanExclusions, LibResBRecoded, conservResB)
outputPolOrientResB <- splitHalf(polOrientSidebySideResB)
outputPolOrientResB$meanr

polOrientSidebySideResC <- select(ResumeDataCleanExclusions, LibResCRecoded, conservResC)
outputPolOrientResC <- splitHalf(polOrientSidebySideResC)
outputPolOrientResC$meanr

## Averaging variables (creating composite variables) that have reliability higher than 0.7
ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>% 
  mutate(American=rowMeans(cbind(likelyAmRes, natEngSkillRes, famAmCustRes,
                                   amCultKnRes, ForAccRecoded, natEngSpRes), na.rm=TRUE),
         Status=rowMeans(cbind(wellEdRes, compRes, critThinkRes,
                                 profSkillRes, highStatRes, profCarRes, qualRes), na.rm=TRUE))
  
```



# Demographics and Exclusions
```{r Demographics and Exclusions}
PNum <- nrow(ResumeDataCleanExclusions)
print(paste("Number of Participants:", PNum))
plyr::count(ResumeDataCleanExclusions$ConsentRecoded)
plyr::count(ResumeDataCleanExclusions$GenderRecoded)
plyr::count(ResumeDataCleanExclusions$RaceRecoded)
```

# Cronbach's Alpha Reliability

## Americanness for each resume

Resume A Americanness: `r AmericanAlphaResA$total$raw_alpha`

Resume B Americanness: `r AmericanAlphaResB$total$raw_alpha`

Resume C Americanness: `r AmericanAlphaResC$total$raw_alpha`

## Status for each resume

Resume A Status: `r StatusAlphaResA$total$raw_alpha`

Resume B Status: `r StatusAlphaResB$total$raw_alpha`

Resume C Status: `r StatusAlphaResC$total$raw_alpha`

# Split-Half Reliability

## Warmth for each resume

Resume A Warmth: `r outputWarmthResA$meanr`

Resume B Warmth: `r outputWarmthResB$meanr`

Resume C Warmth: `r outputWarmthResC$meanr`

## Political orientation for each resume

Resume A Political Orientation: `r outputPolOrientResA$meanr`

Resume B Political Orientation: `r outputPolOrientResB$meanr`

Resume C Political Orientation: `r outputPolOrientResC$meanr`

Summary: The Americanness and status scales had high reliability (>.7) for all resumes so we will create composite (average) variables of those items (questions). The warmth and political orientation scales had low reliability (<.70) for at least 1 resume so we will analyze the items (questions) individually.


# MAIN ANALYSIS
## Americanness One-Way  Between-Subjects ANOVA
```{r Americanness One-Way ANOVA, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=5}
options(knitr.table.format="markdown") 
options(contrasts=c("contr.sum","contr.poly"))

describeBy(ResumeDataCleanExclusions$American, group=ResumeDataCleanExclusions$Condition, mat=TRUE) %>% 
  select(Condition=group1, N=n, Mean=mean, SD=sd, Median=median, Min=min, Max=max, 
         Skew=skew, Kurtosis=kurtosis, SEM=se)  %>% 
  kable(align=c("lrrrrrrrr"), digits=2, row.names=FALSE,
        caption="Americanness of Applicants Descriptive Statistics") %>% 
  kable_styling(bootstrap_options=c("bordered", "responsive","striped"), full_width=TRUE)

boxplot(ResumeDataCleanExclusions$American~ResumeDataCleanExclusions$Condition, 
        main="Americanness by Condition", 
        col= rainbow(4), 
        horizontal=TRUE)

## Create the ANOVA
Americanness.aov <- aov(American ~ Condition, ResumeDataCleanExclusions)

## Plotting assumptions
par(mfrow=c(2,2))
plot(Americanness.aov)

## Plotting residuals
par(mfrow=c(1,1))
# Get the residuals from the model
Americanness.anova.residuals <- residuals(object=Americanness.aov) 
# Create a histogram of the residuals
hist(x=Americanness.anova.residuals) 

## Check normality assumption with Shapiro and Kolmogorov-Smirnov test
shapiro.test(x = Americanness.anova.residuals)
ks.test(Americanness.anova.residuals, "pnorm", mean(Americanness.anova.residuals), sd(Americanness.anova.residuals))

## Check HOV assumption with Brown-Forsyth Test
leveneTest(Americanness.aov)

## Note: Since the normality assumption is violated we run a non-parametric test (Kruskal-Wallis) below
dunn.test(ResumeDataCleanExclusions$American, ResumeDataCleanExclusions$Condition, method = "holm", alpha = 0.05)

## ANOVA results and simple effects
summary(Americanness.aov)
TukeyHSD(Americanness.aov, conf.level=.95)

## Bayesian analysis
ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>% 
  mutate(American=as.numeric(American),
         Condition=as.factor(Condition))

Americanness.bf.aov <- anovaBF(American~Condition, ResumeDataCleanExclusions)
summary(Americanness.bf.aov)
```
Summary: The Kruskal-Wallis test was non-significant (p>.05) and the simple effects between each condition were also non-significant (ps>.05). The ANOVA was also non-significant with non-significant simple effects (ps>.05). The Bayesian analysis indicated an odds of .1222 to 1 (very low odds) that the resumes have different perceived Americanness.


## Status One-Way Between-Subjects ANOVA 
```{r Status One-Way ANOVA, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=5}

describeBy(ResumeDataCleanExclusions$Status, group=ResumeDataCleanExclusions$Condition, mat=TRUE) %>% 
  select(Condition=group1, N=n, Mean=mean, SD=sd, Median=median, Min=min, Max=max, 
         Skew=skew, Kurtosis=kurtosis, SEM=se) %>% 
  kable(align=c("lrrrrrrrr"), digits=2, row.names=FALSE,
        caption="Status of Applicants Descriptive Statistics") %>% 
  kable_styling(bootstrap_options=c("bordered", "responsive","striped"), full_width=FALSE)

boxplot(ResumeDataCleanExclusions$Status~ResumeDataCleanExclusions$Condition, 
        main="Status by Condition", 
        col= rainbow(4), 
        horizontal=TRUE)

# Fitting a linear model 
Status.aov <- aov(Status ~ Condition, ResumeDataCleanExclusions)

## Plotting assumptions
par(mfrow=c(2,2))
plot(Status.aov)

## Plotting residuals
par(mfrow=c(1,1))
# Get the residuals from the model
Status.aov.residuals <- residuals(object=Status.aov) 
# Create a histogram of the residuals
hist(x=Status.aov.residuals) 

## Check normality assumption with Shapiro and Kolmogorov-Smirnov test
shapiro.test(x = Status.aov.residuals)
ks.test(Status.aov.residuals, "pnorm", mean(Status.aov.residuals), sd(Status.aov.residuals))

## Check HOV with Brown-Forsyth Test 
leveneTest(Status.aov)

## Note: Since the normality assumption is violated we run a non-parametric test (Kruskal-Wallis) below
dunn.test(ResumeDataCleanExclusions$Status, ResumeDataCleanExclusions$Condition, method = "holm", alpha = 0.05)

## ANOVA results and simple effects
summary(Status.aov)
TukeyHSD(Status.aov, conf.level=.95)

## Bayesian analysis
ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>% 
  mutate(Status=as.numeric(Status),
         Condition=as.factor(Condition))

Status.bf.aov<- anovaBF(Status~Condition, ResumeDataCleanExclusions)
summary(Status.bf.aov)
```
Summary: The Kruskal-Wallis test was non-significant (p>.05) and the simple effects between each condition were also non-significant (ps>.05). The ANOVA was also non-significant with non-significant simple effects (ps>.05). The Bayesian analysis indicated an odds of .1170 to 1 (very low odds) that the resumes have different perceived status.


## Morality One-Way Between-Subjects ANOVA 
```{r Morality One-Way ANOVA, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=5}

describeBy(ResumeDataCleanExclusions$moralRes, group=ResumeDataCleanExclusions$Condition, mat=TRUE) %>% 
  select(Condition=group1, N=n, Mean=mean, SD=sd, Median=median, Min=min, Max=max, 
         Skew=skew, Kurtosis=kurtosis, SEM=se) %>% 
  kable(align=c("lrrrrrrrr"), digits=2, row.names=FALSE,
        caption="Morality of Applicants Descriptive Statistics") %>% 
  kable_styling(bootstrap_options=c("bordered", "responsive","striped"), full_width=FALSE)

boxplot(ResumeDataCleanExclusions$moralRes~ResumeDataCleanExclusions$Condition, 
        main="Morality by Condition", 
        col= rainbow(4), 
        horizontal=TRUE)

## Fitting a linear model
Morality.aov <- aov(moralRes ~ Condition, ResumeDataCleanExclusions)

## Plotting assumptions
par(mfrow=c(2,2))
plot(Morality.aov)

## Plotting residuals
par(mfrow=c(1,1))
# Get the residuals from the model
Morality.aov.residuals <- residuals(object=Morality.aov) 
# Create a histogram of the residuals
hist(x=Morality.aov.residuals) 

## Check normality assumption with Shapiro and Kolmogorov-Smirnov tests
shapiro.test(x = Morality.aov.residuals)
ks.test(Morality.aov.residuals, "pnorm", mean(Morality.aov.residuals), sd(Morality.aov.residuals))

## Check HOV with Brown-Forsyth Test
leveneTest(Morality.aov)

## Note: Since the normality assumption is violated we run a non-parametric test (Kruskal-Wallis) below
dunn.test(ResumeDataCleanExclusions$moralRes, ResumeDataCleanExclusions$Condition, method = "holm", alpha = 0.05)

## ANOVA results and simple effects
summary(Morality.aov)
TukeyHSD(Morality.aov, conf.level=.95)

## Bayesian analysis
ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>% 
  mutate(moralRes=as.numeric(moralRes),
         Condition=as.factor(Condition))

Morality.bf.aov<- anovaBF(moralRes~Condition, ResumeDataCleanExclusions)
summary(Morality.bf.aov)
```
Summary: The Kruskal-Wallis test was non-significant (p>.05) and the simple effects between each condition were also non-significant (ps>.05). The ANOVA was also non-significant with non-significant simple effects (ps>.05). The Bayesian analysis indicated an odds of .0786 to 1 (very low odds) that the resumes have different perceived morality.



## Friendliness One-Way Between-Subjects ANOVA
```{r Friendliness One-Way ANOVA, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=5}

describeBy(ResumeDataCleanExclusions$friendRes, group=ResumeDataCleanExclusions$Condition, mat=TRUE) %>% 
  select(Condition=group1, N=n, Mean=mean, SD=sd, Median=median, Min=min, Max=max, 
         Skew=skew, Kurtosis=kurtosis, SEM=se) %>% 
  kable(align=c("lrrrrrrrr"), digits=2, row.names=FALSE,
        caption="Friendliness of Applicants Descriptive Statistics") %>% 
  kable_styling(bootstrap_options=c("bordered", "responsive","striped"), full_width=FALSE)

boxplot(ResumeDataCleanExclusions$friendRes~ResumeDataCleanExclusions$Condition,
        main="Friendliness by Condition", 
        col= rainbow(4), 
        horizontal=TRUE)

## Fitting a linear model
Friendly.aov <- aov(friendRes ~ Condition, ResumeDataCleanExclusions)

## Plotting assumptions
par(mfrow=c(2,2))
plot(Friendly.aov)

## Plotting residuals
par(mfrow=c(1,1))
# Get the residuals from the model
Friendly.aov.residuals <- residuals(object=Friendly.aov) 
# Create a histogram of the residuals
hist(x=Friendly.aov.residuals) 

## Check normality assumption with Shapiro and Kolmogorov-Smirnov tests
shapiro.test(x = Friendly.aov.residuals)
ks.test(Friendly.aov.residuals, "pnorm", mean(Friendly.aov.residuals), sd(Friendly.aov.residuals))

## Check HOV with Brown-Forsyth Test
leveneTest(Friendly.aov)

## Note: Since the normality assumption is violated we run a non-parametric test (Kruskal-Wallis) below
dunn.test(ResumeDataCleanExclusions$friendRes, ResumeDataCleanExclusions$Condition, method = "holm", alpha = 0.05)

## ANOVA results and simple effects
summary(Friendly.aov)
TukeyHSD(Friendly.aov, conf.level=.95)

## Bayesian analysis
ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>% 
  mutate(friendRes=as.numeric(friendRes),
         Condition=as.factor(Condition))

Friendly.bf.aov<- anovaBF(friendRes~Condition, ResumeDataCleanExclusions)
summary(Friendly.bf.aov)
```
Summary: The Kruskal-Wallis test was non-significant (p>.05) and the simple effects between each condition were also non-significant (ps>.05). The ANOVA was also non-significant with non-significant simple effects (ps>.05). The Bayesian analysis indicated an odds of .1571 to 1 (very low odds) that the resumes have different perceived friendliness.

## Liberal One-Way Between-Subjects ANOVA
```{r Liberal One-Way ANOVA, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=5}

describeBy(ResumeDataCleanExclusions$libRes, group=ResumeDataCleanExclusions$Condition, mat=TRUE) %>% 
  select(Condition=group1, N=n, Mean=mean, SD=sd, Median=median, Min=min, Max=max, 
         Skew=skew, Kurtosis=kurtosis, SEM=se) %>% 
  kable(align=c("lrrrrrrrr"), digits=2, row.names=FALSE,
        caption="Liberal Political Orientation of Applicants Descriptive Statistics") %>% 
  kable_styling(bootstrap_options=c("bordered", "responsive","striped"), full_width=FALSE)

boxplot(ResumeDataCleanExclusions$libRes~ResumeDataCleanExclusions$Condition, 
        main="Liberal Political Orientation by Condition", 
        col= rainbow(4), 
        horizontal=TRUE)

## Fitting a linear model
Liberal.aov <- aov(libRes ~ Condition, ResumeDataCleanExclusions)

## Plotting assumptions
par(mfrow=c(2,2))
plot(Liberal.aov)

## Plotting residuals
par(mfrow=c(1,1))
# Get the residuals from the model
Liberal.aov.residuals <- residuals(object=Liberal.aov) 
# Create a histogram of the residuals
hist(x=Liberal.aov.residuals) 

## Check normality assumption with Shapiro and Kolmogorov-Smirnov tests
shapiro.test(x = Liberal.aov.residuals)
ks.test(Liberal.aov.residuals, "pnorm", mean(Liberal.aov.residuals), sd(Liberal.aov.residuals))

## Check HOV with Brown-Forsyth Test
leveneTest(Liberal.aov)

## Note: Since the normality assumption is violated we run a non-parametric test (Kruskal-Wallis) below
dunn.test(ResumeDataCleanExclusions$libRes, ResumeDataCleanExclusions$Condition, method = "holm", alpha = 0.05)

## ANOVA results and simple effects
summary(Liberal.aov)
TukeyHSD(Liberal.aov, conf.level=.95)

## Bayesian analysis
ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>% 
  mutate(libRes=as.numeric(libRes),
         Condition=as.factor(Condition))

Liberal.bf.aov<- anovaBF(libRes~Condition, ResumeDataCleanExclusions)
summary(Liberal.bf.aov)
```
Summary: The Kruskal-Wallis test was non-significant (p>.05) and the simple effects between each condition were also non-significant (ps>.05). The ANOVA was also non-significant with non-significant simple effects (ps>.05). The Bayesian analysis indicated an odds of .0968 to 1 (very low odds) that the resumes have different perceived liberal political orientation.

## Conservative One-Way Between-Subjects ANOVA
```{r Conservative One-Way ANOVA, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=5}

describeBy(ResumeDataCleanExclusions$conservRes, group=ResumeDataCleanExclusions$Condition, mat=TRUE) %>% 
  select(Condition=group1, N=n, Mean=mean, SD=sd, Median=median, Min=min, Max=max, 
         Skew=skew, Kurtosis=kurtosis, SEM=se) %>% 
  kable(align=c("lrrrrrrrr"), digits=2, row.names=FALSE,
        caption="Conservative Political Orientation of Applicants Descriptive Statistics") %>% 
  kable_styling(bootstrap_options=c("bordered", "responsive","striped"), full_width=FALSE)

boxplot(ResumeDataCleanExclusions$conservRes~ResumeDataCleanExclusions$Condition, 
        main="Conservative Political Orientation by Condition", 
        col= rainbow(4), 
        horizontal=TRUE)

## Fitting a linear model
Conservative.aov <- aov(conservRes ~ Condition, ResumeDataCleanExclusions)

## Plotting assumptions
par(mfrow=c(2,2))
plot(Conservative.aov)

## Plotting residuals
par(mfrow=c(1,1))
# Get the residuals from the model
Conservative.aov.residuals <- residuals(object=Conservative.aov) 
# Create a histogram of the residuals
hist(x=Conservative.aov.residuals) 

## Check normality assumption with Shapiro and Kolmogorov-Smirnov tests
shapiro.test(x = Conservative.aov.residuals)
ks.test(Conservative.aov.residuals, "pnorm", mean(Conservative.aov.residuals), sd(Conservative.aov.residuals))

## Check HOV with Brown-Forsyth Test
leveneTest(Conservative.aov)

## Note: Since the normality assumption is violated we run a non-parametric test (Kruskal-Wallis) below
dunn.test(ResumeDataCleanExclusions$conservRes, ResumeDataCleanExclusions$Condition, method = "holm", alpha = 0.05)

## ANOVA results and simple effects
summary(Conservative.aov)
TukeyHSD(Conservative.aov, conf.level=.95)

## Bayesian analysis
ResumeDataCleanExclusions <- ResumeDataCleanExclusions %>% 
  mutate(conservRes=as.numeric(conservRes),
         Condition=as.factor(Condition))

Conservative.bf.aov<- anovaBF(conservRes~Condition, ResumeDataCleanExclusions)
summary(Conservative.bf.aov)
```
Summary: The Kruskal-Wallis test was non-significant (p>.05) and the simple effects between each condition were also non-significant (ps>.05). The ANOVA was also non-significant with non-significant simple effects (ps>.05). The Bayesian analysis indicated an odds of .1180 to 1 (very low odds) that the resumes have different perceived conservative political orientation.

## Overall Summary: 

The resumes did not significantly differ in how they were perceived along status, Americanness, friendliness, morality, and liberal and conservative political orientation scales.
